---
title: 'Demo: multivariate analysis for inflow data'
author: "Nan-Jung Hsu"
date: "2020/5/21"
output: html_document
---

### Lake Shasta Inflow Data (source: Textbook: SS)

Data: data `climhyd` have 454 months of measured values for the climatic
variables air temperature, dew point, cloud cover, wind speed, precipitation, and inflow, at Lake Shasta. 

Goal: look at possible relations between the weather factors and the inflow to Lake Shasta.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preparation
R packages for multivariate time series analysis:

* vars
* MTS
* mAr 

```{r warning=FALSE, message=FALSE}
library(vars)
library(astsa)
#library(MTS)
```

### EDA (focusing on inflow and precipitation)

```{r, fig.align='center'}
data(climhyd)
head(climhyd)
colnames(climhyd)

pairs(climhyd[,6:1], pch=16, cex=0.3, col=4)
```


```{r, fig.align='center', fig.height=8, fig.width=10}
#par(mfcol=c(4,1))
#for (i in c(6,1,3,5)){ts.plot(climhyd[,i]);title(colnames(climhyd)[i])}

par(mfcol=c(2,1))
ts.plot(climhyd[,6], ylab="", lwd=2); title(colnames(climhyd)[6])
ts.plot(climhyd[,5], ylab="", lwd=2); title(colnames(climhyd)[5])
```

Data transformation

```{r, fig.align='center', fig.height=8, fig.width=10}
x = climhyd[,6:5]

x[,1] = log(x[,1])   # log(inflow)
x[,2] = sqrt(x[,2])  # sqrt(precipitation)

par(mfcol=c(2,1))
ts.plot(x[,1])
ts.plot(x[,2])
```


```{r}
summary(x)
```


```{r, fig.align='center', fig.height=8, fig.width=10}
acf(x)
pacf(x)
```

```{r, fig.align='center', fig.height=6, fig.width=8}
par(mfcol=c(1,1))
ccf(x[,1], x[,2], main="Inflow & Precip")
```

### Vector AR model fitting

* VAR(2) with constant mean 
* VAR(2) with seasonal mean (dummy for 12 months) 
* AIC-selected VAR with constant mean (or seasonal mean)
* some model diagnostics

VAR(2) is not good due to strong seasonality shown in residuals!

```{r, fig.align='center', fig.height=8, fig.width=10}
fit1 = VAR(x,p=2)
summary(fit1)

plot(fit1,names="Inflow")
plot(fit1,names="Precip")
```

VAR(2) with seasonal mean effects (period = 12) 

* After taking into account seasonality, precipitation is not correlated to lag values of inflow! (which make more common sense)

* Minor lack-of-fit with dependence left in residuals

```{r}

fit2 = VAR(x, p=2, season=12)
summary(fit2)

#coef(fit2)    #call partial output
#resid(fit2)
#fitted(fit2)
```


```{r, fig.align='center', fig.height=8, fig.width=10}
plot(fit2,names="Inflow")  #diagnostics plots
plot(fit2,names="Precip")    

normality.test(fit2)  #normality checking
serial.test(fit2,lags.pt=12) #Portmanteau test 
arch.test(fit2)       #ARCH effect test

predict(fit2,12)
plot(predict(fit2,12), lwd=2)

```

AIC-selected VAR(p) (p.max = 10) with seasonal mean effects (period = 12) 

* with seasonal mean:
  + VAR(4) is selected by AIC, FPE, HQ
  + VAR(2) is selected by BIC (SC)

* with constant mean:
  + higher order model is required, e.g., VAR(9) 
  
Note: Model (order) selection is crucial for multivariate time series analysis!!

```{r, fig.align='center', fig.height=6, fig.width=8}
fit.aic = VARselect(x,10,season=12)

par(mfcol=c(1,1))
ts.plot(t(fit.aic$crit[1:3,]), col=1:3, lwd=2, xlab="AR Order")
abline(v=fit.aic$sel[1:3],lty=2,col=1:3,lwd=2)
legend("topleft",legend=rownames(fit.aic$crit[1:3,]),col=1:3,lty=1, bty="n")
title("Information Criteria")


fit.aic = VARselect(x,10) #no seasonality
par(mfcol=c(1,1))
ts.plot(t(fit.aic$crit[1:3,]), col=1:3, lwd=2, xlab="AR Order")
abline(v=fit.aic$sel[1:3],lty=2,col=1:3,lwd=2)
legend("topleft",legend=rownames(fit.aic$crit[1:3,]),col=1:3,lty=1, bty="n")
title("Information Criteria")
```

Summary for AIC-selected model 

```{r, fig.align='center', fig.height=8, fig.width=10}
fit3 = VAR(x, p=4, season=12)
summary(fit3)

plot(fit3,names="Inflow")  #diagnostics plots
plot(fit3,names="Precip")    

serial.test(fit3,lags.pt=12) #Portmanteau test 
arch.test(fit3)              #ARCH effect test
#apply(resid(fit3),2,hist)    #check normality


fit3.pred = predict(fit3, n.ahead=24, ci=0.95)
plot(fit3.pred, lwd=2)
```

### Test for Granger Causality 

* `Precip` Granger-cause `Inflow`
* `Inflow` do not Granger-cause `Precip`
* instantaneous causality exists between `Precip` and `Inflow`

```{r}
causality(fit3, cause= "Precip") #specify cause and target variables
causality(fit3, cause= "Inflow")
```

### Impulse response function analysis for VAR model 


```{r, fig.align='center', fig.height=6, fig.width=8}
a = irf(fit3, response = "Inflow", n.ahead = 24, ortho=FALSE, boot = TRUE)
plot(a, names="Inflow")
plot(a, names="Precip")

a = irf(fit3, response = "Precip", n.ahead = 24, ortho=FALSE, boot = TRUE)
plot(a, names="Inflow")
plot(a, names="Precip")

a = irf(fit3, response = "Inflow", n.ahead = 24, ortho=TRUE, boot = TRUE) #orthogonal IRF
plot(a, names="Inflow")
plot(a, names="Precip")

```

### Parameter-constrained fitting (set zero constraints on parameters)

Further enhance the fitted model by removing insignificant parameters. 

* setup threshold for t ratio (e.g., |t|=2) and refit the model
* manually setup the constrained matrix (0-1 matrix)

```{r}
summary(fit3)
fit3.constrained = restrict(fit3, method="ser", thresh=2.0)
summary(fit3.constrained)  

round(Bcoef(fit3.constrained),digit=3)

#setup the constrained matrix:
R1 = (Bcoef(fit3.constrained)!=0)
R1 = matrix(as.numeric(R1), nrow=2)

fit3.constrained = restrict(fit3, method="manual", resmat=R1) 
round(Bcoef(fit3.constrained),digit=3)

```

