---
title: "Demo: Target tracking using state space model"
date: "2020/5/28"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
#load package
library(astsa)
library(latex2exp) #latex
```


#### Simulated data to mimic the trajectory of a moving object.

* observed 2-dim location: $y_t=x_t+\epsilon_t$ (it has measurement error)
* true 2-dim location: $x_t=x_{t-1}+(v+\eta_t)$
* 2-dim speed at time t: $v+\eta_t$ (whih is around the mean speed v with some variation)


```{r, fig.height=5, fig.width=7}
n=30
v = c(1,1)*0.5 #mean speed
x = matrix(0,n,2)
eps = 0.5*matrix(rnorm(n*2),n,2) #measurement error
eta = 0.2*matrix(rnorm(n*2),n,2) #speed variation
for (i in 2:n) {
  x[i,] = x[i-1,]+v+eta[i,]
}

y = x+eps

par(mfcol=c(1,1))
plot(y,xlab="x-loc", ylab="y-loc", pch=3, cex=0.8, lwd=2) 
lines(x, col=2, pch=16) #true signal
legend("topleft",legend=c("true signal","noisy obs'n"),col=c(2,1),pch=c(16,3), bty="n")
```

#### Assuming Random level model (2-dim) with given system matrices

* $y_t = A x_t + \epsilon_t, \epsilon_t\sim N(0,R)$
* $x_t = \Phi x_{t-1}+ \eta_t, \eta\sim N(0,Q)$
* set $A=I_2, \Phi=I_2, R=Q=I_2$
* check filter/predictor/smoother for tracking the true location 

```{r, fig.height=5, fig.width=7}
A = diag(2)
mu0 = y[1,]
Sigma0 = var(y)
Phi = diag(2)
cQ = diag(2)
cR = diag(2)

y.Kf = Kfilter0(n,y,A,mu0,Sigma0,Phi,cQ,cR)
y.sm = Ksmooth0(n,y,A,mu0,Sigma0,Phi,cQ,cR) 

par(mfcol=c(1,1))
plot(y,xlab="x-loc", ylab="y-loc", pch=3, lwd=2, cex=0.8) 
lines(x, col=2, pch=16) #true signal
points(x[1,1],x[1,2],col=2, pch=16, cex=1.8) 
lines(t(y.Kf$xf[,1,]),col=3, pch=16)  #filter value
lines(t(y.sm$xs[,1,]),col=4, pch=16) #smoother
legend("topleft",legend=c("true signal","filter","smoother","noisy obs'n"),col=c(2,3,4,1),pch=c(16,16,16,3), bty="n")
```

#### Assuming Random level & slope model (2-dim) with unknown system parameters

\begin{eqnarray*}
\mbox{measurement eq:} \quad y_t &=& (I_2,0_2) \left(\begin{array}{c} x_t \\ v_t \end{array}\right) +\epsilon_t, \epsilon_t\sim N(0,R),\\
\mbox{state eq:} \quad 
\left(\begin{array}{c} x_t \\ v_t \end{array}\right) &=& \left(\begin{array}{cc} I_2 & I_2 \\ 0 & I_2 \end{array}\right)\left(\begin{array}{c} x_t \\ v_t \end{array}\right) + w_t, w_t\sim N(0,Q).
\end{eqnarray*}

* write a function for computing -logL via Kalman filter
* estimate parameters to minimize -logL

```{r, fig.height=5, fig.width=7}
#Random loc + speed
n = nrow(y)
#A = array(cbind(diag(2),0,0), dim=c(2,4,n))
A = cbind(diag(2),0,0)
mu0 = c(y[1,],y[2,]-y[1,])
Sigma0 = diag(4)  
Phi = cbind(rbind(diag(2),diag(0,2)), rbind(diag(2),diag(2)))


# Function to Calculate -logL
#y:nx2
tracking.neglogL = function(para){
  cQ = matrix(0,4,4)
  cQ[!lower.tri(cQ)] = para[1:10]
  cR = matrix(0,2,2)
  cR[!lower.tri(cR)] = para[11:13]
  kf = Kfilter0(n,y,A,mu0,Sigma0,Phi,cQ,cR)
  return(kf$like) 
}


cQ.init = diag(0.2,4)
cR.init = diag(0.3,2)

init.par = c(cQ.init[!lower.tri(cQ.init)],cR.init[!lower.tri(cR.init)])  # initial values of parameters

est = optim(init.par, tracking.neglogL, method="BFGS", hessian=TRUE, control=list(trace=1,REPORT=1))

names(est) #check output

cQ = matrix(0,4,4)
cQ[!lower.tri(cQ)] = est$par[1:10]
t(cQ)%*%cQ

cR = matrix(0,2,2)
cR[!lower.tri(cR)] = est$par[11:13]
t(cR)%*%cR
```

#### compute the filtered values, predicted values and smoothed values and their variances.

```{r, fig.height=5, fig.width=7}
y.Kf = Kfilter0(n,y,A,mu0,Sigma0,Phi,cQ,cR)
y.sm = Ksmooth0(n,y,A,mu0,Sigma0,Phi,cQ,cR) 

par(mfcol=c(1,1))
plot(y,xlab="x-loc", ylab="y-loc", pch=3, lwd=2, cex=0.8) 
lines(x, col=2, pch=16) #true signal
points(x[1,1],x[1,2],col=2, pch=16, cex=1.8) 
lines(t(y.Kf$xf[,1,]),col=3, pch=16)  #filter value
lines(t(y.sm$xs[,1,]),col=4, pch=16) #smoother
legend("topleft",legend=c("true signal","filter","smoother","noisy obs'n"),col=c(2,3,4,1),pch=c(16,16,16,3), bty="n")


#plot true speed vs estimated speed:
ts.plot(t(y.sm$xs[3:4,1,]), col=1:2)
abline(h=v, col=3)
```







